---
title: "Final_Project - Regression and Classification A"
author: "Binghan Zheng"
date: "3/29/2022"
output: html_document
---
# SetUp

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Libraries

```{r}
library(tidyverse)
library(fastDummies)
library(caret)
```

#Preparing the Data

```{r}
df_all <- readr::read_csv("final_project_train.csv", col_names = TRUE)
df_all <- dummy_cols(df_all, select_columns = 'region')
df_all <- dummy_cols(df_all, select_columns = 'customer')
df_all$log_response <- log(df_all$response)
df_all<-df_all %>% 
  mutate(outcome = ifelse(outcome == 'event', 1,0))
df_all
```

#Model 1 Categorical Linear Additive

```{r, eval =TRUE}
mod1 <- lm( log_response ~ region_XX + region_YY + region_ZZ + customer_A + customer_B + customer_D + customer_E + customer_G + customer_K + customer_M +  customer_Other + customer_Q, data = df_all)
```

#Model 2 Continuous: Linear Additive 

```{r ,eval=TRUE}
mod2 <- lm( log_response ~ xa_01 + 
              xa_02 + xa_03 + xa_04 + xa_05 + xa_06 + xa_07 + xa_08 +
              
              xb_01 + xb_02 +  xb_03 + xb_04 + xb_05 + xb_06 +  xb_07 + xb_08 +
              
              xs_01 + xs_02 + xs_03 + xs_04 + xs_05 + xs_06 +
              
              xn_01 + xn_02 + xn_03 + xn_04 + xn_05 + xn_06 + xn_07 + xn_08 +
              
              xw_01 + xw_02 + xw_03 , data = df_all)


```

#Model 3: Categorial and Continuous Linear Additive

```{r,eval =TRUE}
mod3 <- lm( response ~ 
              region_XX + region_YY + region_ZZ + 
              customer_A + customer_B + customer_D + customer_E + customer_G + customer_K + customer_M + 
              customer_Other + customer_Q + xa_01 + 
              xa_02 + xa_03 + xa_04 + xa_05 + xa_06 + xa_07 + xa_08 +
              xb_01 + xb_02 +  xb_03 + xb_04 + xb_05 + xb_06 +  xb_07 + xb_08 +
              xs_01 + xs_02 + xs_03 + xs_04 + xs_05 + xs_06 +
              xn_01 + xn_02 + xn_03 + xn_04 + xn_05 + xn_06 + xn_07 + xn_08 +
              xw_01 + xw_02 + xw_03, data = df_all)

```

#Model 4: Categorical vs Continuous Interactions Linear Additive: Region

```{r,eval =TRUE}
mod4 <- lm( log_response ~ 
              (xa_01 + xa_02 + xa_03 + xa_04 + xa_05 + xa_06 + xa_07 + xa_08 + xb_01 + xb_02 +  xb_03 + xb_04 + xb_05 + xb_06 +  xb_07 + xb_08 + xs_01 + xs_02 + xs_03 + xs_04 + xs_05 + xs_06 + xn_01 + xn_02 + xn_03 + xn_04 + xn_05 + xn_06 + xn_07 + xn_08 + xw_01 + xw_02 + xw_03) *
  (region_XX + region_YY + region_ZZ), data = df_all)

```

#Model 5: Categorical vs Continuous Interactions Linear Additive: Customer

```{r,eval =TRUE}
mod5 <- lm( log_response ~ 
              
              (xa_01 +xa_02 + xa_03 + xa_04 + xa_05 + xa_06 + xa_07 + xa_08 + xb_01 + xb_02 +  xb_03 + xb_04 + xb_05 + xb_06 +  xb_07 + xb_08 + xs_01 + xs_02 + xs_03 + xs_04 + xs_05 + xs_06 + xn_01 + xn_02 + xn_03 + xn_04 + xn_05 + xn_06 + xn_07 + xn_08 + xw_01 + xw_02 + xw_03) *
  (customer_A + customer_B + customer_D + customer_E + customer_G + customer_K + customer_M +  customer_Other + customer_Q), data = df_all)
```

#Model 6: All Pairwise Interaction

```{r,eval =TRUE}
mod6 <- lm( log_response ~ (xa_01 + 
              xa_02 + xa_03 + xa_04 + xa_05 + xa_06 + xa_07 + xa_08 +
              xb_01 + xb_02 +  xb_03 + xb_04 + xb_05 + xb_06 +  xb_07 + xb_08 +
              xs_01 + xs_02 + xs_03 + xs_04 + xs_05 + xs_06 +
              xn_01 + xn_02 + xn_03 + xn_04 + xn_05 + xn_06 + xn_07 + xn_08 +
              xw_01 + xw_02 + xw_03)^2 , data = df_all)
```

#Model 7

```{r}
df_a <- 3
df_b <- 3
df_s <- 3
df_n <- 3
df_w <- 3

mod7 <- lm( log_response ~ 
              
              splines::ns(xa_01, df_a) + splines::ns(xa_02, df_a) + splines::ns(xa_03, df_a) +
              splines::ns(xa_04, df_a) +
              splines::ns(xa_05, df_a) + splines::ns(xa_06, df_a) + splines::ns(xa_07, df_a) +
              splines::ns(xa_08, df_a) +
              
              splines::ns(xb_01, df_b) + splines::ns(xb_02, df_b) +  splines::ns(xb_03, df_b) +
              splines::ns(xb_04, df_b) +
              splines::ns(xb_05, df_b) + splines::ns(xb_06, df_b) +  splines::ns(xb_07, df_b) +
              splines::ns(xb_08, df_b) + 
              
              splines::ns(xs_01, df_s) + splines::ns(xs_02, df_s) + splines::ns(xs_03, df_s) +
              splines::ns(xs_04, df_s) +
              splines::ns(xs_05, df_s) + splines::ns(xs_06, df_s) +
              
              splines::ns(xn_01, df_n) + splines::ns(xn_02, df_n) + splines::ns(xn_03, df_n) +
              splines::ns(xn_04, df_n) +
              splines::ns(xn_05, df_n) + splines::ns(xn_06, df_n) + splines::ns(xn_07, df_n) +
              splines::ns(xn_08, df_n) +
      
              splines::ns(xw_01, df_w) + splines::ns(xw_02, df_w) + splines::ns(xw_03, df_w),
              data = df_all)

```


#Model 8 - Splines Interact Customer

```{r}
df_a <- 3
df_b <- 3
df_s <- 3
df_n <- 3
df_w <- 3

mod8 <- lm( log_response ~ 
              (splines::ns(xa_01, df_a) + splines::ns(xa_02, df_a) +
              splines::ns(xa_03, df_a) + splines::ns(xa_04, df_a) +
              splines::ns(xa_05, df_a) + splines::ns(xa_06, df_a) +
              splines::ns(xa_07, df_a) + splines::ns(xa_08, df_a) +
                
              splines::ns(xb_01, df_b) + splines::ns(xb_02, df_b) + 
              splines::ns(xb_03, df_b) + splines::ns(xb_04, df_b) +
              splines::ns(xb_05, df_b) + splines::ns(xb_06, df_b) +
              splines::ns(xb_07, df_b) + splines::ns(xb_08, df_b) + 
                
              splines::ns(xs_01, df_s) + splines::ns(xs_02, df_s) +
              splines::ns(xs_03, df_s) + splines::ns(xs_04, df_s) +
              splines::ns(xs_05, df_s) + splines::ns(xs_06, df_s) +
                
              splines::ns(xn_01, df_n) + splines::ns(xn_02, df_n) +
              splines::ns(xn_03, df_n) + splines::ns(xn_04, df_n) +
              splines::ns(xn_05, df_n) + splines::ns(xn_06, df_n) +
              splines::ns(xn_07, df_n) + splines::ns(xn_08, df_n) +
                
              splines::ns(xw_01, df_w) + splines::ns(xw_02, df_w) +
              splines::ns(xw_03, df_w)) *
                
  (customer_A + customer_B + customer_D + customer_E + customer_G +
  customer_K + customer_M +  customer_Other + customer_Q),
    data = df_all)
```

#Model 9 - Splines Interact Region

```{r}
df_a <- 3
df_b <- 3
df_s <- 3
df_n <- 3
df_w <- 3


mod9 <- lm( log_response ~ 
              
      (splines::ns(xa_01, df_a) +splines::ns(xa_02, df_a) + splines::ns(xa_03, df_a) + splines::ns(xa_04, df_a) +
      splines::ns(xa_05, df_a) + splines::ns(xa_06, df_a) + splines::ns(xa_07, df_a) + splines::ns(xa_08, df_a) +
              
      splines::ns(xb_01, df_b) + splines::ns(xb_02, df_b) +  splines::ns(xb_03, df_b) + splines::ns(xb_04, df_b)+ splines::ns(xb_05, df_b) + splines::ns(xb_06, df_b) +  splines::ns(xb_07, df_b) + splines::ns(xb_08, df_b) + 
              
  splines::ns(xs_01, df_s) + splines::ns(xs_02, df_s) + splines::ns(xs_03, df_s) + splines::ns(xs_04, df_s) +
  splines::ns(xs_05, df_s) + splines::ns(xs_06, df_s) +
              
  splines::ns(xn_01, df_n) + splines::ns(xn_02, df_n) + splines::ns(xn_03, df_n) + splines::ns(xn_04, df_n) +
  splines::ns(xn_05, df_n) + splines::ns(xn_06, df_n) + splines::ns(xn_07, df_n) + splines::ns(xn_08, df_n) +
              
  splines::ns(xw_01, df_w) + splines::ns(xw_02, df_w) + splines::ns(xw_03, df_w)) *
  (region_XX + region_YY + region_ZZ),
    
  data = df_all)
```

#Model Evaluation

```{r, eval=TRUE}
mod_performace<-bind_rows(
broom::glance(mod1),
broom::glance(mod2),
broom::glance(mod3),
broom::glance(mod4),
broom::glance(mod5),
broom::glance(mod6),
broom::glance(mod7),
broom::glance(mod8),
broom::glance(mod9))

mod_performace
```

##Top 3 Model Coef Plot

#Best Model

- Performance Metric Used in Determining the best models: R-Squared.

Reasoning: I want to focus around determining the strength of the correlation between the predictors and the response. In focusing around these models of high r-squared values, we can also narrow down those predictors which are most significant of which, according to the plot(varImp(mod8)) are: 


```{r, fig.width=30, fig.height=30}
# Mod 8
coefplot::coefplot(mod8)
```

#Second Best Model

```{r, fig.width=30, fig.height=30}
# Mod 6
coefplot::coefplot(mod6)
```

#Third Best Model

```{r, fig.width=20, fig.height=20}
# Mod 4
coefplot::coefplot(mod9)
```

How do coefficient summaries compare between the 3 models?

- All of the coefficient summaries between the 3 models contain many variables which are not statistically significant yet do contain intervals which are very wide ranging and highly uncertain. Our best model, mod 8, does contain smaller intervals around 0, but are still not entirely significant. I will next utilize `train` in determining those variables which were important and noteworthy enough in the best model, mod8.

Which inputs seem important?

- Let's find out with some quick tests

```{r}
set.seed(12345)
my_ctrl <- caret::trainControl(method = "repeatedcv",
                               number = 5,
                               repeats = 3,
                               savePredictions = TRUE)
my_metric <- "Rsquared"
```

```{r,warning = FALSE, message = FALSE}
mod8<- train(log_response ~ 
              (splines::ns(xa_01, 3) + splines::ns(xa_02, 3) +
              splines::ns(xa_03, 3) + splines::ns(xa_04, 3) +
              splines::ns(xa_05, 3) + splines::ns(xa_06, 3) +
              splines::ns(xa_07, 3) + splines::ns(xa_08, 3) +
                
              splines::ns(xb_01, 3) + splines::ns(xb_02, 3) + 
              splines::ns(xb_03, 3) + splines::ns(xb_04, 3) +
              splines::ns(xb_05, 3) + splines::ns(xb_06, 3) +
              splines::ns(xb_07, 3) + splines::ns(xb_08, 3) + 
                
              splines::ns(xs_01, 3) + splines::ns(xs_02, 3) +
              splines::ns(xs_03, 3) + splines::ns(xs_04, 3) +
              splines::ns(xs_05, 3) + splines::ns(xs_06, 3) +
                
              splines::ns(xn_01, 3) + splines::ns(xn_02, 3) +
              splines::ns(xn_03, 3) + splines::ns(xn_04, 3) +
              splines::ns(xn_05, 3) + splines::ns(xn_06, 3) +
              splines::ns(xn_07, 3) + splines::ns(xn_08, 3) +
                
              splines::ns(xw_01, 3) + splines::ns(xw_02, 3) +
              splines::ns(xw_03, 3)) *
                
  (customer_A + customer_B + customer_D + customer_E + customer_G +
  customer_K + customer_M +  customer_Other + customer_Q), 
                    data = df_all, 
                    method = "lm", 
                    metric = my_metric, 
                    preProcess = c("center" , "scale"),
                    trControl = my_ctrl,
                    trace = FALSE)
```

```{r}
plot(varImp(mod8), top = 10)
```

- Those continuous variables which were significantly important in our model are in descending order: xs_02, xs_01, xa_03 and xb_08. These four are repeated multiple times and I will consider these variables to be our most important inputs. 



###CLASSIFICATION

#Model 1: Categorical Linear Additive

```{r}
mod1 <- glm( outcome ~ region_XX + region_YY + region_ZZ + customer_A + customer_B + customer_D + customer_E + customer_G + customer_K + customer_M +  customer_Other + customer_Q, family = "binomial", data = df_all)


```

#Model 2: Continuous Linear Additive

```{r}

mod2 <- glm( outcome ~ xa_01 + 
              xa_02 + xa_03 + xa_04 + xa_05 + xa_06 + xa_07 + xa_08 +
              
              xb_01 + xb_02 +  xb_03 + xb_04 + xb_05 + xb_06 +  xb_07 + xb_08 +
              
              xs_01 + xs_02 + xs_03 + xs_04 + xs_05 + xs_06 +
              
              xn_01 + xn_02 + xn_03 + xn_04 + xn_05 + xn_06 + xn_07 + xn_08 +
              
              xw_01 + xw_02 + xw_03 ,family = "binomial", data = df_all)


```

#Model 3: Continuous and Categorical Linear Additive

```{r}

mod3 <- glm( outcome ~ 
              region_XX + region_YY + region_ZZ + 
              
              customer_A + customer_B + customer_D + customer_E + customer_G + customer_K + customer_M +  customer_Other + customer_Q +
xa_01 + 
              xa_02 + xa_03 + xa_04 + xa_05 + xa_06 + xa_07 + xa_08 +
              
              xb_01 + xb_02 +  xb_03 + xb_04 + xb_05 + xb_06 +  xb_07 + xb_08 +
              
              xs_01 + xs_02 + xs_03 + xs_04 + xs_05 + xs_06 +
              
              xn_01 + xn_02 + xn_03 + xn_04 + xn_05 + xn_06 + xn_07 + xn_08 +
              
              xw_01 + xw_02 + xw_03, family = "binomial",data = df_all)


```

#Model 4: Categorical vs Continuous Interactions Linear Additive: Region

```{r}

mod4 <- glm( outcome ~ 
              (xa_01 + xa_02 + xa_03 + xa_04 + xa_05 + xa_06 + xa_07 + xa_08) *
  (region_XX + region_YY + region_ZZ) +
              
              (xb_01 + xb_02 +  xb_03 + xb_04 + xb_05 + xb_06 +  xb_07 + xb_08) * 
  (region_XX + region_YY + region_ZZ) +
              
              (xs_01 + xs_02 + xs_03 + xs_04 + xs_05 + xs_06)*
  (region_XX + region_YY + region_ZZ) +
              
              (xn_01 + xn_02 + xn_03 + xn_04 + xn_05 + xn_06 + xn_07 + xn_08)*
  (region_XX + region_YY + region_ZZ) +
              
              (xw_01 + xw_02 + xw_03)*
  (region_XX + region_YY + region_ZZ), family = "binomial", data = df_all)

```

#Model 5: Categorical vs Continuous Interactions Linear Additive: Customer

```{r}

mod5 <- glm( outcome ~ 
              
              (xa_01 +xa_02 + xa_03 + xa_04 + xa_05 + xa_06 + xa_07 + xa_08) *
  (customer_A + customer_B + customer_D + customer_E + customer_G + customer_K + customer_M +  customer_Other + customer_Q) +
              
              (xb_01 + xb_02 +  xb_03 + xb_04 + xb_05 + xb_06 +  xb_07 + xb_08) * 
  (customer_A + customer_B + customer_D + customer_E + customer_G + customer_K + customer_M +  customer_Other + customer_Q) +
              
              (xs_01 + xs_02 + xs_03 + xs_04 + xs_05 + xs_06)*
  (customer_A + customer_B + customer_D + customer_E + customer_G + customer_K + customer_M +  customer_Other + customer_Q) +
              
              (xn_01 + xn_02 + xn_03 + xn_04 + xn_05 + xn_06 + xn_07 + xn_08)*
  (customer_A + customer_B + customer_D + customer_E + customer_G + customer_K + customer_M +  customer_Other + customer_Q) +
              
              (xw_01 + xw_02 + xw_03)*
  (customer_A + customer_B + customer_D + customer_E + customer_G + customer_K + customer_M +  customer_Other + customer_Q), family = "binomial",data = df_all)

```

#Model 6: All Pairwise Interaction

```{r}

mod6 <- glm( outcome ~ (xa_01 + 
              xa_02 + xa_03 + xa_04 + xa_05 + xa_06 + xa_07 + xa_08 +
              
              xb_01 + xb_02 +  xb_03 + xb_04 + xb_05 + xb_06 +  xb_07 + xb_08 +
              
              xs_01 + xs_02 + xs_03 + xs_04 + xs_05 + xs_06 +
              
              xn_01 + xn_02 + xn_03 + xn_04 + xn_05 + xn_06 + xn_07 + xn_08 +
              
              xw_01 + xw_02 + xw_03)^2 , family = "binomial", data = df_all)


```

#Model 7: Spline of Continuous

```{r}
df_a <- 2
df_b <- 2
df_s <- 2
df_n <- 2
df_w <- 2

mod7 <- glm( outcome ~ 
              
              splines::ns(xa_01, df_a) +splines::ns(xa_02, df_a) + splines::ns(xa_03, df_a) + splines::ns(xa_04, df_a) +
              splines::ns(xa_05, df_a) + splines::ns(xa_06, df_a) + splines::ns(xa_07, df_a) + splines::ns(xa_08, df_a) +
              
              splines::ns(xb_01, df_b) + splines::ns(xb_02, df_b) +  splines::ns(xb_03, df_b) + splines::ns(xb_04, df_b) +
              splines::ns(xb_05, df_b) + splines::ns(xb_06, df_b) +  splines::ns(xb_07, df_b) + splines::ns(xb_08, df_b) + 
              
              splines::ns(xs_01, df_s) + splines::ns(xs_02, df_s) + splines::ns(xs_03, df_s) + splines::ns(xs_04, df_s) +
              splines::ns(xs_05, df_s) + splines::ns(xs_06, df_s) +
              
              splines::ns(xn_01, df_n) + splines::ns(xn_02, df_n) + splines::ns(xn_03, df_n) + splines::ns(xn_04, df_n) +
              splines::ns(xn_05, df_n) + splines::ns(xn_06, df_n) + splines::ns(xn_07, df_n) + splines::ns(xn_08, df_n) +
              
              splines::ns(xw_01, df_w) + splines::ns(xw_02, df_w) + splines::ns(xw_03, df_w), family = "binomial", data = df_all)



```

#Model 8: Spline of Continuous Interact Region

```{r,warning = FALSE, message = FALSE}
df_a <- 2
df_b <- 2
df_s <- 2
df_n <- 2
df_w <- 2

mod8 <- glm( outcome ~ 
              
              (splines::ns(xa_01, df_a) +splines::ns(xa_02, df_a) + splines::ns(xa_03, df_a) + splines::ns(xa_04, df_a) +
              splines::ns(xa_05, df_a) + splines::ns(xa_06, df_a) + splines::ns(xa_07, df_a) + splines::ns(xa_08, df_a) +
              
              splines::ns(xb_01, df_b) + splines::ns(xb_02, df_b) +  splines::ns(xb_03, df_b) + splines::ns(xb_04, df_b) +
              splines::ns(xb_05, df_b) + splines::ns(xb_06, df_b) +  splines::ns(xb_07, df_b) + splines::ns(xb_08, df_b) + 
              
              splines::ns(xs_01, df_s) + splines::ns(xs_02, df_s) + splines::ns(xs_03, df_s) + splines::ns(xs_04, df_s) +
              splines::ns(xs_05, df_s) + splines::ns(xs_06, df_s) +
              
              splines::ns(xn_01, df_n) + splines::ns(xn_02, df_n) + splines::ns(xn_03, df_n) + splines::ns(xn_04, df_n) +
              splines::ns(xn_05, df_n) + splines::ns(xn_06, df_n) + splines::ns(xn_07, df_n) + splines::ns(xn_08, df_n) +
              
              splines::ns(xw_01, df_w) + splines::ns(xw_02, df_w) + splines::ns(xw_03, df_w)) *
  (customer_A + customer_B + customer_D + customer_E + customer_G + customer_K + customer_M +  customer_Other + customer_Q),
    
    family = "binomial", data = df_all)


```

#Model 9: Spline of Continuous Interact Customer

```{r,warning = FALSE, message = FALSE}
df_a <- 2
df_b <- 2
df_s <- 2
df_n <- 2
df_w <- 2

mod9 <- glm( outcome ~ 
              
              (splines::ns(xa_01, df_a) +splines::ns(xa_02, df_a) + splines::ns(xa_03, df_a) + splines::ns(xa_04, df_a) +
              splines::ns(xa_05, df_a) + splines::ns(xa_06, df_a) + splines::ns(xa_07, df_a) + splines::ns(xa_08, df_a) +
              
              splines::ns(xb_01, df_b) + splines::ns(xb_02, df_b) +  splines::ns(xb_03, df_b) + splines::ns(xb_04, df_b) +
              splines::ns(xb_05, df_b) + splines::ns(xb_06, df_b) +  splines::ns(xb_07, df_b) + splines::ns(xb_08, df_b) + 
              
              splines::ns(xs_01, df_s) + splines::ns(xs_02, df_s) + splines::ns(xs_03, df_s) + splines::ns(xs_04, df_s) +
              splines::ns(xs_05, df_s) + splines::ns(xs_06, df_s) +
              
              splines::ns(xn_01, df_n) + splines::ns(xn_02, df_n) + splines::ns(xn_03, df_n) + splines::ns(xn_04, df_n) +
              splines::ns(xn_05, df_n) + splines::ns(xn_06, df_n) + splines::ns(xn_07, df_n) + splines::ns(xn_08, df_n) +
              
              splines::ns(xw_01, df_w) + splines::ns(xw_02, df_w) + splines::ns(xw_03, df_w)) *
  (region_XX + region_YY + region_ZZ),
    
    family = "binomial", data = df_all)

```

#Model Evaluation
```{r, eval=TRUE}
mod_performace<-bind_rows(
broom::glance(mod1),
broom::glance(mod2),
broom::glance(mod3),
broom::glance(mod4),
broom::glance(mod5),
broom::glance(mod6),
broom::glance(mod7),
broom::glance(mod8),
broom::glance(mod9))

mod_performace
```

##Top 3 Model Coef Plot

#Best Model

```{r, fig.width=30, fig.height=30}

coefplot::coefplot(mod9)
```

#Second Best Model

```{r, fig.width=30, fig.height=30}
# Mod 6
coefplot::coefplot(mod8)
```

#Third Best Model

```{r, fig.width=20, fig.height=20}
# Mod 4
coefplot::coefplot(mod5)
```